### 2024-10-07 draft-2/draft-2.tex
added the quit message

A client message has one of eight types indicated by the first token of the
message (\s{uci}, \s{debug}, \s{setoption}, \s{ucinewgame}, \s{position},
\s{isready}, \s{go}, and \s{stop}).

@@

An engine message has one of six types indicated by the first token of the
message (\s{id}, \s{option}, \s{uciok}, \s{info}, \s{readyok}, \s{bestmove}).

@@

% Empty messages may always be sent and must be ignored by the client
% and engine. Empty messages never cause a transition.

@@

% This specification stops governing the interaction between the client
% and the engine when the client sends a well-formed quit message in
% the idle state. Engines are recommended to shut down and terminate
% themselves. Clients are recommended to provide a grace period before
% killing the engine.

>>>>

A client message has one of nine types indicated by the first token of the
message (\s{uci}, \s{debug}, \s{setoption}, \s{ucinewgame}, \s{position},
\s{isready}, \s{go}, \s{stop}, and \s{quit}).

@@

An engine message has one of six types indicated by the first token of
the message (\s{id}, \s{option}, \s{uciok}, \s{info}, \s{readyok}, and
\s{bestmove}).

@@

@@

\minor The specification ceases to govern the interaction between the client
and the engine when the client enqueues a well-formed \s{quit} message.
\vskip-\parskip
\bluebox{Engines are recommended to stop searching immediately and exit.
Clients are recommended, if engines are their subprocesses, to provide a
grace period before terminating engines.}
